---
title: " College tuition on a geographic scale"
author: Chante Hamilton
format:
 html:
  theme: yeti
excecute:
 eval: false
 echo: false
---


```{r}
#| echo: false
#| output: false
library(tidyverse)
library(gtsummary)
tuition_income_data <- read_csv(here::here("data","tuition_income.csv"))
col_types = cols(campus = col_factor(levels = c("On Campus",
																								"Off Campus")), income_lvl = col_factor(levels = c("0 to 30000",
																																																	 "30001 to 48000", "48001 to 75000",																																																	 "75001 to 110000", "Over 110000")))
```

# Table of Descriptive Statistics

```{r}
#| echo: false
#| label: tbl-one
#| tbl-cap: "Characteristics by choice of residency"
#| output-location: slide
table1 <- tbl_summary(
	tuition_income_data,
	by = campus,
	include = c(state, income_lvl, net_cost),
	label = list(
		state ~ "State name",
		income_lvl ~ "Income level",
		net_cost ~ "Average net cost"
	),
	missing_text = "Missing")|>
	add_p(test = list(all_continuous() ~ "t.test",
										all_categorical() ~ "chisq.test")) |>
	add_overall(col_label = "**Total**") |>
	bold_labels() |>
	modify_footnote(update = everything() ~ NA) |>
	modify_header(label = "**Variable**", p.value = "**P**") 
table1
inline_text(table1, variable = "net_cost", column = "On Campus")
stats <- list(n = nrow(tuition_income_data),
							mean_il = mean(tuition_income_data$net_cost, na.rm = TRUE))
```
@tbl-one This is a table of characteristics by choice of residency while in college. 

The average net cost for students who choose to live on campus is `r stats$mean_il`

## Multivariable Regression Analysis 

```{r}
#| echo: false
linear_model <- lm(net_cost ~ income_lvl + campus + state,
									 data = tuition_income_data)
```

```{r}
#| echo: false
#| #| label: tbl-two
#| tbl-cap: "Multivariable linear regression model"
#| output-location: slide
table2 <-tbl_regression(
	linear_model,
	intercept = TRUE,
	label = list(
		income_lvl ~ "Income level",
		campus ~ "On or off-campus",
		state ~ "State name"
	))
```
@tbl-two This is a table showing a multivariable analysis of net cost on income level, campus residency, and state name. 

## Barplot of Income level

```{r}
#| echo: false
#| label: fig-bar
#| fig-cap: "This barplot shows the frequency of students in each income bracket"
ggplot(data.frame(tuition_income_data$income_lvl), aes(x=tuition_income_data$income_lvl)) +
	geom_bar()
```

